---
title: "Dataset Transfomations"
author: "LSE Candidate Number: 50799"
date: "Autumn Term 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This function performs an input transformation on a dataset and returns the transformed data.
More specifically, it normalizes the numeric columns to take values between 0 and 1.
```{r transformation_1}
transf1 <- function(data){
  # find columns with numeric data
  # sapply only returns a logical vector with TRUEs and FALSEs, not the column names
  numeric_cols <- names(data)[sapply(data, is.numeric)]
  
  # loop through columns
  for (col in numeric_cols) {
    
    # find minimum and maximum values for scale
    min_val <- min(data[[col]])
    max_val <- max(data[[col]])
    
    # apply normalization formula
    data[[col]] <- (data[[col]]-min_val)/max_val
  }
  
  #return transformed data
  return(data)
}
```

The dataset I have chosen to work on is 'Iris', which includes a series of measurements from different species of iris flowers.

Here I apply the normalization transformation to the Iris dataset:
```{r output}
transf1(iris)
```

